Verifying Demonstrations

### 2018-08-28 paper/adversary-model.tex
Streamlines the adversary models

One reason to not allow \(S\) to learn \(P\)'s identity is that for this 
communication \(P\) has options, such as \ac{Tor}, for anonymous communication.
However, given a strong enough adversary, such anonymous communication might 
not be possible.
Hence the following definition.

@@

\begin{definition}[Base identity--location adversary]%
  \label{base-identity-location-adversary}
  The witness \(W\) and the protester \(P\) communicate.
  They learn some protocol data \(d_{W,P}(W, l)\) and the time it took place, 
  \(t_{P,W}\).
  The witness later communicates with \(S\), where \(S\) only learns 
  \(f(d_{W,P}(W, l))\), for some function \(f\), and the time it happened, 
  \(t_{W,S}\).
  The adversary controls \(S\).
  The adversary wins if he can link \(W\) and \(l\).
\end{definition}

\Cref{base-identity-location-adversary} is the analogous to 
\cref{base-identity-cause-adversary}.
\Cref{fig:identity-location-adversary} illustrates the roles and relations.

@@

The base rationale is the same as for \cref{base-identity-cause-adversary}, the 
witness \(W\) can submit to \(S\) over an anonymous channel, such as \ac{Tor}.
Anyone who is in the same location will learn that \(W\) was present, we want 
to prevent anyone \emph{not present} to learn that \(W\) was there --- hence we 
do not consider the protester as part of the adversary, only \(S\).
We thus conclude with the strongest adversary against the witness.

\begin{definition}[Strongest witness adversary]%
  \label{strongest-identity-location-adversary}
  Things are the same as in \cref{base-identity-location-adversary}, except 
  that \(S\) learns the witness' identity \(W\).
\end{definition}

>>>>

One reason to not allow \(S\) to learn \(P\)'s identity is that for this 
communication \(P\) has options, such as \ac{Tor}, for anonymous communication.
However, given a strong enough adversary, such anonymous communication might 
not be possible.
We capture such a strong adversary in the following definition.

@@

\begin{definition}[Base identity--location adversary]%
  \label{base-identity-location-adversary}
  The adversary controls \(S\).
  The witness \(W\) and the protester \(P\) communicate.
  They learn some protocol data \(d_{W,P}(W, l)\) and \(d_{W,P}(P,l)\) and the 
  time it took place, \(t_{P,W}\).
  \begin{description}
    \item[The witness case:]
      The witness later communicates with \(S\), where \(S\) only learns 
      \(f(d_{W,P}(W, l))\), for some function \(f\), and the time it happened, 
      \(t_{W,S}\).
      The adversary wins if he can link \(W\) and \(l\).
    \item[The protester case:]
      The protester later communicates with \(S\), where \(S\) only learns 
      \(g(d_{W,P}(P, l))\), for some function \(g\), and the time it happened, 
      \(t_{P,S}\).
      The adversary wins if he can link \(P\) and \(l\).
  \end{description}
\end{definition}

\Cref{fig:identity-location-adversary} illustrates the roles and relations.

@@

The base rationale is the same as for \cref{base-identity-cause-adversary}, the 
witness \(W\) can submit to \(S\) over an anonymous channel, such as \ac{Tor}.
Anyone who is in the same location will learn that \(W\) was present, we want 
to prevent anyone \emph{not present} to learn that \(W\) was there --- hence we 
do not consider the protester as part of the adversary, only \(S\).
Analogous to the identity--cause adversary, we conclude with the strongest 
identity--location adversary.

\begin{definition}[Strongest identity--location adversary]%
  \label{strongest-identity-location-adversary}
  Things are the same as in \cref{base-identity-location-adversary}, except 
  that \(S\) learns the witness' and protester's identities \(W\) and \(P\), in 
  the respective cases.
\end{definition}
